---
title: "Grand Valley Magazine Project"
author: "Matthew Dickinson & Foster Thorburn"
date: "`r Sys.Date()`"
output: pdf_document
---

# Data Import
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r packages, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(readr)
library(flextable)
library(ggthemes)
library(kableExtra)
library(forcats)
library(htmltools)
library(webshot)
```


```{r data, warning = FALSE}
gvm_data <- read_csv("GVM_data.csv")
head(gvm_data) |> 
  select(seq(1, 51, 11)) |>
  select(-4) |>
  flextable() |>
  autofit() |>
  fit_to_width(7.5)
```

# Question Breakdown

Establishing number of people per age group.
```{r number people, echo=FALSE, warning = FALSE}
age_group_nums <- gvm_data |>
  group_by(age) |>
  summarize(number_in_age_group = n())

age_table <- age_group_nums |>
  rename(Age = age, "Number in category" = number_in_age_group) |>
  flextable() |>
  width(
    j = "Number in category",
    width = 1.5
  )

gvm_data$age <- as.factor(gvm_data$age)

age_table
```

```{r setting globally theme, include = FALSE}
theme_set(theme_bw())
theme_default <- theme(
    axis.ticks = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_blank())
```


## Question 1
Asks `Where do you acquire most of your information about GVSU?` and is a mark all that apply question.

```{r Question 1 data}
Q1_numbers <- gvm_data |>
  select(starts_with("most_info_")) |>
  pivot_longer(cols = starts_with("most_info_"), names_to = "location", values_to = "selection") |>
  group_by(location) |>
  summarize(num_in_category = sum(selection, na.rm = TRUE)) |>
  mutate(location = str_replace_all(str_replace_all(location, "most_info_", ""), "_", " "),
         location = str_to_title(location),
         location = str_replace_all(location, "Gvm", "GVM"),
         location = str_replace_all(location, "Gv", "GV"),
         location = case_when(
           location == "Wordofmouth Alumni" ~ "Word of Mouth",
           location == "Socialmedia" ~ "Social Media",
           TRUE ~ location
         ))
  
Q1_data <- gvm_data |>
  select(age, starts_with("most_info_")) |>
  pivot_longer(!age, names_to = "location", values_to = "selection") |>
  mutate(location = str_replace_all(str_replace_all(location, "most_info_", ""), "_", " "),
         location = str_to_title(location),
         location = str_replace_all(location, "Gvm", "GVM"),
         location = str_replace_all(location, "Gv", "GV"),
         location = case_when(
           location == "Wordofmouth Alumni" ~ "Word of Mouth",
           location == "Socialmedia" ~ "Social Media",
           TRUE ~ location
         )) |>
  group_by(age, location) |>
  summarize(count = sum(selection, na.rm = TRUE)) |>
  left_join(age_group_nums, by = "age") |>
  mutate(age_percent = (count/number_in_age_group)*100,
         age = as.factor(age),
         location = as.factor(location)) |>
  left_join(Q1_numbers) |>
  mutate(category_percent = (count/num_in_category)*100)
```


```{r Question 1 plot}
Q1_plot <- Q1_data |>
  ggplot(aes(fct_reorder(location, (num_in_category)), category_percent, fill = forcats::fct_rev(age))) +
  geom_col(position = "dodge", color = "black", linewidth = .1) +
  coord_flip() +
  scale_fill_viridis_d() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(
    x = "Location",
    y = "Percent",
    title = "Where do you acquire most of your information about GV?",
    fill = "Age Group"
  ) +
  theme_default +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line())

print(Q1_plot)
```


Here are the counts per each category for Question 1.
```{r Question 1 counts}
tab_q1 <- Q1_numbers |> 
  rename(Location = location, "Count in category" = num_in_category) |> 
  flextable() |>
  width(
    j = "Location",
    width = 1.5)

tab_q1
```


## Question 3
Asks `How many PRINT issues have you read within the last year?` and is single select.
```{r Question 3 data}
Q3_numbers <- gvm_data |>
  group_by(num_issues) |>
  summarize(num_in_category = n())

Q3_data <- gvm_data |>
  select(age, num_issues) |>
  group_by(age, num_issues) |>
  summarize(count = n()) |>
  left_join(age_group_nums) |>
  left_join(Q3_numbers) |>
  mutate(
    age_percent = (count/number_in_age_group)*100,
    issues_percent = (count/num_in_category)*100)
```


```{r Question 3 plot}
Q3_plot <- Q3_data |>
  ggplot(aes((num_issues), issues_percent, fill = forcats::fct_rev(age))) +
  geom_col(position = "dodge", color = "black", linewidth = .1) +
  scale_fill_viridis_d() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(
    x = "Number of Issues",
    y = "Percent",
    fill = "Age Group",
    title = "How many PRINT issues have you read within the last year?"
  ) + 
  theme_default

print(Q3_plot)
```

Here is a table of counts per category for Question 3.
```{r Question 3 counts}
tab_q3 <- Q3_numbers |> 
  rename("Number of issues" = num_issues, "Count in category" = num_in_category) |>
  flextable()

tab_q3
```



## Question 5 
Asks `To what extent do you agree or disagree with these statements about PRINTED issues of Grand Valley Magazine?` and is a likert matrix, where a score of `1` means `Strongly Disagree` and `5` means `Strongly Agree.`

The questions are:


* I **enjoy** reading the printed publication.

* The **design** and visual elements aid in my understanding and enjoyment of the text.

* I feel more **connected** to Grand Valley State University after the print issues.

* Reading print issues of Grand Valley Magazine makes me **proud** to be part of the GVSU community.


```{r Question 5 data}
Q5_numbers <- gvm_data |>
  select(starts_with("print_")) |>
  pivot_longer(starts_with("print_"), names_to = "category", values_to = "score") |>
  mutate(category = str_to_title(str_remove_all(str_replace_all(str_replace_all(category, "print_", ""), "_", " "), "likert"))) |>
  group_by(category, score) |>
  summarize(number_selction = n())

Q5_data <- gvm_data |>
  select(age, starts_with("print_")) |>
  pivot_longer(!age, names_to = "category", values_to = "score") |>
  mutate(category = str_to_title(str_remove_all(str_replace_all(str_replace_all(category, "print_", ""), "_", " "), "likert"))) |>
  group_by(age, category, score) |>
  summarise(number = n()) |>
  left_join(Q5_numbers) |>
  left_join(age_group_nums) |>
  mutate(
    category_score_percent = (number/number_selction)*100,
    category_age_percent = (number/number_in_age_group)*100,
    score = as.factor(case_when(
      score == 1 ~ "Strongly Disagree",
      score == 2 ~ "Disagree",
      score == 3 ~ "Neutral",
      score == 4 ~ "Agree",
      TRUE ~ "Strongly Agree"
    )))

Q5_data$score <- factor(Q5_data$score, levels = c("Strongly Disagree", "Disagree", "Neutral", "Agree", "Strongly Agree"))
```


```{r Question 5 plot}
Q5_plot <- Q5_data |> 
  ggplot(aes(category, category_age_percent, fill = as.factor(score))) +
  geom_col(position = "dodge", color = "black", linewidth = .1) +
  scale_fill_viridis_d(direction = -1) +
  scale_y_continuous(expand = expansion(mult = c(0, .1))) +
  labs(
    x = "Question Type",
    y = "Percent", 
    fill = "Agreement",
    title = "To what extent do you agree or disagree with these statements about PRINTED \nissues of Grand Valley Magazine?"
  ) +
  facet_grid(~age) +
  theme_default +
  theme(
    axis.text.x = element_text(angle = 45, hjust = .65, vjust = .75),
    legend.position = "bottom")
  

# make box plot to identify spread
  # no because it was an interval scale
# proportion in each age group

print(Q5_plot)
```

```{r Question 5 counts}
tab_q5 <- Q5_numbers |>
  rename(Type = category, Score = score, "Number in category" = number_selction) |>
  flextable() |>
  width(
    j = "Number in category",
    width = 1.25
  )

tab_q5
```



## Question 7
Asks `How many articles have you read on the Grand Valley Magazine WEBSITE in the last year?`

```{r Question 7 data}
Q7_numbers <- gvm_data |>
  group_by(num_articles) |>
  summarize(num_in_category = n())

Q7_data <- gvm_data |>
  select(age, num_articles) |>
  group_by(age, num_articles) |>
  summarize(count = n()) |>
  left_join(age_group_nums) |>
  left_join(Q7_numbers) |>
  mutate(
    age_percent = (count/number_in_age_group)*100,
    articles_percent = (count/num_in_category)*100) 

# Q7_data |>
#   # filter(age == "17-24") |>
#   filter(num_articles == 0) |>
#   # pull(age_percent) |>
#   pull(articles_percent) |>
#   sum()
```

```{r Question 7 plot}
Q7_plot <- Q7_data |> 
  ggplot(aes(as.factor(num_articles), articles_percent, fill = forcats::fct_rev(age))) +
  geom_col(position = "dodge", color = "black", linewidth = .1) +
  scale_fill_viridis_d() +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(
    x = "Number of Articles",
    y = "Percent",
    fill = "Age Group",
    title = "How many articles have you read on the Grand Valley Magazine \nWEBSITE in the last year?",
    caption = "Note: 15 indicates 10+ articles"
  ) +
  theme_default

print(Q7_plot)
```


Here is a table of number of articles per category for question 7.
```{r Question 7 counts}
tab_q7 <- Q7_numbers |> 
  rename("Number of articles" = num_articles, "Count in category" = num_in_category) |>
  flextable() |>
  width(
    j = "Number of articles",
    width = 1
  )

tab_q7
```



## Question 9
Asks `Would you read Grand Valley Magazine if it was offered as a WEBSITE version only?`


```{r Question 9 data}
Q9_numbers <- gvm_data |>
  mutate(website_only = case_when(
           website_only == "I don't know/I'm not sure" ~ "Unsure",
           TRUE ~ website_only
         )) |>
  group_by(website_only) |>
  summarize(num_in_category = n())
  
Q9_data <- gvm_data |>
  select(age, website_only) |>
  group_by(age, website_only) |>
  summarize(count = n()) |>
  left_join(age_group_nums) |>
  mutate(age_percent = (count/number_in_age_group)*100,
         website_only = case_when(
           website_only == "I don't know/I'm not sure" ~ "Unsure",
           TRUE ~ website_only
         )) |>
  left_join(Q9_numbers) |>
  mutate(category_percent = (count/num_in_category)*100)
```

```{r Question 9 plot}
Q9_plot <- Q9_data |>
  ggplot(aes(forcats::fct_rev(as.factor(website_only)), category_percent, fill = forcats::fct_rev(age))) +
  geom_col(position = "dodge", color = "black", linewidth = .1) +
  scale_fill_viridis_d() +
  scale_y_continuous(breaks = seq(0, 50, 5), expand = expansion(mult = c(0, .1))) +
  labs(
    y = "Percent",
    fill = "Age Group",
    title = "Would you read Grand Valley Magazine if it was offered as a WEBSITE \nversion only?"
  ) +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "none") +
  facet_grid(~age) +
  theme_default

# five by three chi-square test
# divide by total number of people in that CATEGORY
# post hoc to find differences

print(Q9_plot)
```


Here is a table of counts for question 9.
```{r Question 9 counts}
tab_q9 <- Q9_numbers |> 
  rename("Read GVM if website only" = website_only, "Count in category" = num_in_category) |>
  flextable() |>
  width(
    j = "Read GVM if website only",
    width = 1.5
  )


tab_q9
```




## Question 11
Asks `What actions have you taken as a result of reading Grand Valley Magazine?` and was a mark all that apply.


```{r Question 11 data}
Q11_numbers <- gvm_data |>
  select(starts_with("action_")) |>
  pivot_longer(starts_with("action_"), names_to = "action", values_to = "selection") |>
  mutate(action = str_to_title(str_replace_all(str_replace_all(action, "action_", ""), "_", " " )),
         action = case_when(
           action == "Recommended Gv" ~ "Recommended GV",
           action == "Shared Article Social Media" ~ "Shared Article - Social Media",
           action == "Shared Article Email" ~ "Shared Article - Email",
           TRUE ~ action
         )) |>
  group_by(action) |>
  summarize(num_in_category = sum(selection, na.rm = TRUE))

Q11_data <- gvm_data |>
  select(age, starts_with("action_")) |>
  pivot_longer(!age, names_to = "action", values_to = "selection") |>
  mutate(action = str_to_title(str_replace_all(str_replace_all(action, "action_", ""), "_", " " )),
         action = case_when(
           action == "Recommended Gv" ~ "Recommended GV",
           action == "Shared Article Social Media" ~ "Shared Article - Social Media",
           action == "Shared Article Email" ~ "Shared Article - Email",
           TRUE ~ action
         )) |>
  group_by(age, action) |>
  summarize(count = sum(selection, na.rm = TRUE)) |>
  left_join(age_group_nums) |>
  left_join(Q11_numbers) |>
  mutate(age_percent = (count/number_in_age_group)*100,
         action = as.factor(action),
         category_percent = (count/num_in_category)*100)
```


```{r Question 11 plot}
Q11_plot <- Q11_data |>
  filter(action != "None") |>
  ggplot(aes(fct_reorder(action, (category_percent)), category_percent, fill = forcats::fct_rev(age))) +
  geom_col(position = "dodge", color = "black", linewidth = .1) +
  scale_y_continuous(expand = expansion(mult=c(0, 0.1))) +
  coord_flip() +
  scale_fill_viridis_d() +
  labs(
    x = "Action",
    y = "Percent",
    fill = "Age Group",
    title = "What actions have you taken as a result of reading the \nGrand Valley Magazine?"
  ) +
  theme_default +
  theme(panel.grid.major.y = element_blank(),
        panel.grid.major.x = element_line())

# divide not by num people in age but by num people in category
print(Q11_plot)
```

Table of counts per category for question 11.
```{r Question 11 counts}
tab_q11 <- Q11_numbers |> 
  rename(Action = action, "Count in category" = num_in_category) |>
  flextable(cwidth = 1.25, cheight = 1.25)

tab_q11
```


# Exporting plots and tables
```{r exporting plots, warning = FALSE}
plot_list <- list(Q1_plot, Q3_plot, Q5_plot, Q7_plot, Q9_plot, Q11_plot)

for (i in seq_along(plot_list)){
  
  plot_num = seq(1, 12, 2)[i]
  
  file_name_svg = paste0("Q", plot_num, "_plot", ".svg")
  file_name_png = paste0("Q", plot_num, "_plot", ".png")
  
  ggsave(
    filename=file_name_svg,
    plot=plot_list[[i]],
    device="svg",
    path="~/MyR/GVM-Project/plots",
    width=7, height=5, units="in")
  
  ggsave(
    filename=file_name_png,
    plot=plot_list[[i]],
    device="png",
    path="~/MyR/GVM-Project/plots",
    width=7, height=5, units="in")
}
```

```{r exporting tables, message = FALSE, warning=FALSE, include=FALSE}
count_tables <- list(tab_q1, tab_q3, tab_q5, tab_q7, tab_q9, tab_q11)

for (i in seq_along(count_tables)){

  table_num = seq(1, 12, 2)[i]

  table_name = paste0("Q", table_num, "_table")

  path_svg = paste0("~/MyR/GVM-Project/tables/", table_name, ".svg")
  path_png = paste0("~/MyR/GVM-Project/tables/", table_name, ".png")


  save_as_image(
    count_tables[[i]],
    path = path_svg)

  save_as_image(
    count_tables[[i]],
    path = path_png)
  
  # print(table_name)
  # print(path_svg)
  # print(path_png)
  # print(table_num)
  
  
}

save_as_image(
  age_table,
  path = "~/MyR/GVM-Project/tables/age_table.png"
)

save_as_image(
  age_table,
  path = "~/MyR/GVM-Project/tables/age_table.svg"
)
```

```{r fake success table for pdf version}
data.frame(
  Plot = c("Question 1", "Question 3", "Question 5", "Question 7", "Question 9", "Question 11"),
  Status = rep("Export Successful", 6)
) |> flextable(cwidth = 1.5)
```

